\chapter{Accreditation Request}

\section{Institution}
\rubric{Provide the full name under which the Institution operates and confers the qualifications resulting from the programs to be accredited.} 

\begin{centering}
\begin{tabular}{l l}\hline
\toprule
Name of Institution	& The University of Western Australia \\
CEO	Vice-Chancellor & XXX \\
Institution Address	& XXX\\
Telephone &	XXX\\
Institution Web Site &	\href{https://www.uwa.edu.au/home}{UWA Web Site}\\
\bottomrule
\end{tabular}
\end{centering}






\section{ICT Teaching Entity}
\rubric{Provide details of the college/faculty/school/department structure responsible for
offering the program(s) for accreditation. Room is provided to allow a three-level description of the organisation entity - please provide the type of entity (e.g. faculty or department) and its name (e.g. School of Computing and Mathematical Sciences).}

\begin{centering}
\begin{tabular}{l l}\hline
%\multicolumn{2}{l}{\large\bf\cellcolor{colorDarkBlue} ICT Teaching Entity} \\ %\hline
\toprule
ICT Teaching Entity & \\ \midrule
Level 1	&   School of Physics, Mathematics and Computing\\
Level 2 & Department of Computer Science and Software Engineering\\ 
ICT Teaching Entity	& Department of Computer Science and Software Engineering\\
ICT Entity Web Site &	\href{}{Department Web Site}\\ \midrule
Contact Information & \\ \midrule
Head ICT Teaching Entity & XXX \\
Address	& XXX\\
Telephone &	XXX\\
E-mail Address	& 
\href{mailto:XXX}{XXX}\\ %\hline

Industry Liaison Coordinator & School Operations Coordinator \href{mailto:XXX}{XXX}\\

\bottomrule
\end{tabular}
\end{centering}

\section{Programs}
\rubric{Provide a list of programs submitted for accreditation.
Level refers to the level of award (e.g. AQF 7, AQF 9).
Type refers to the ACS accreditation sought (Professional, Specialist).}

%\begin{table}[h]
\begin{centering}
%\begin{tabular}{| P{9cm} | c | c | c |}\hline
\begin{tabular}{ P{9cm} ccc}\hline
%\multicolumn{4}{l}{\large\bf\cellcolor{colorDarkBlue} Programs} \\ %\hline
\toprule
{\bf Title of Program}  & {\bf Campus}  & {\bf Level} & {\bf Type} \\ 
\midrule
Bachelor of Science (Computer Science major) & Crawley & AQF 7 & P    \\ %\hline
\bottomrule
\end{tabular}
\end{centering}


\section{Institution Contact}
\rubric{Provide details of the primary contact and person responsible for this application: Name,TItle,Address,Telephone,Email}

\begin{centering}
\begin{tabular}{l l}\hline
%\multicolumn{2}{l}{\large\bf\cellcolor{colorDarkBlue} Institution Contact} \\ %\hline
\toprule
Name	& XXX\\
Title	& Accreditation Officer\\
Address	& XXX\\
Telephone Number(s) &	XXX\\
E-mail Address	& 
\href{mailto:XXX}{XXX}\\
\bottomrule
\end{tabular}
\end{centering}


\section{School Staffing}
\rubric{Provide the following staffing table for the main campus. If the information is provided in the online
staff directory for the ICT School then that may be provided instead. Note All staff are teaching on the Crawley campus only.
Permanent/Contract Staff only (i.e. non casual or sessional – see below). }

\subsection*{Academic Staff in Computer Science}
\begin{footnotesize}
\input{Tables/StaffCVs.tex}
\end{footnotesize}

\vspace{.25cm}
\noindent
{Click on staff names for links to their Staff Profile pages}



\subsection*{Casual Staff} % and Sessional

\rubric{Where casual or sessional staff are lecturing or in charge of hybrid/blended learning classes as opposed to just taking tutorials or laboratories, fill in the table below.}




